POMDP comparisons across sigma_m, sigma_g

### 2017-10-06 appendix/appendixB.Rmd
cleaner code

<!--- ICK, find a more streamlined way to do this stuff species by species -->

Convert example data into discrete index space.

```{r}
ex <- examples %>%
  mutate(biomass = index(scaled_biomass, states),          
         catch = index(scaled_catch, actions))  %>% 
  select(year, biomass, catch, commonname)
```

@@

  pars %>% 
  rowwise() %>% 
  do(statics(.)) %>% 
  right_join(ex) %>% 
  ungroup()  -> ex2

  ex2
```

@@

historical <- ex2 %>% 
  group_by(commonname) %>% 
  mutate(det =  det_f(S_star, biomass),
         msy =  msy_f(F_MSY, biomass),
         pgy =  pgy_f(F_PGY, biomass)) %>%
  mutate_if(is.integer, rescale, N=N) %>%
  select(year, biomass, catch, det, msy, pgy, commonname)
```

>>>>

@@

policy_pars <- 
  pars %>% 
  rowwise() %>% 
  do(statics(.))
```  
  Convert example data into discrete index space.

```{r}
ex <- examples %>%
  mutate(biomass = index(scaled_biomass, states),          
         catch = index(scaled_catch, actions))  %>% 
  left_join(policy_pars) %>% 
  ungroup()

@@

historical <- ex %>% 
  group_by(commonname) %>% 
  mutate(det =  det_f(S_star, biomass),
         msy =  msy_f(F_MSY, biomass),
         pgy =  pgy_f(F_PGY, biomass)) %>%
  mutate_if(is.integer, rescale, N=N) %>%
  select(year, biomass, catch, det, msy, pgy, commonname)
```

Plot
